---
title: "Meta_Analisi.Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19). \\pkg{foo}"
author: "Rai Puig & Jordi Real"
website: "https://github.com/USR-DAPCAT/"

date: "`r format(Sys.time(), '%d %B, %Y')`"


output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    fig_caption: true
    css: logos_css/usr_styles.css
  pdf_document: default
  word_document: default
  
  bibliography: references.bib 
---

&nbsp;
<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<img src=\"https://www.idiapjgol.org/images/logo.png\" style=\"float: right ;width: 130px;\"/>')
     $head.prepend('<img src=\"https://avatars2.githubusercontent.com/u/57066591?s=200&v=4\" style=\"margin-left:25% ;width: 80px;\"/>')
     $head.prepend('<img src=\"logos_css/logoDAP_Cat.png\" style=\"float: left:1;width: 185px;\"/>')
   });
</script>


<div class="watermark">DRAFT</div>

****



# 0. State:

**Latest updates** 

> July/2022

**Done**

* Meta_Analisi Associations of macrovascular complications DM and Covid-19: UK,France,HM(Spain),Barcelona

* MODEL1::[Meta-Analysis of Death ~ Macrovascular disease (unadjusted)]
* MODEL2::[Meta-Analysis of Death ~ Macrovascular disease + Age + Sex]
* MODEL3::[Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease] 
* MODEL4::[Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia]

* MODEL1::[Meta-Analysis of Uci ~ Macrovascular disease (unadjusted)]
* MODEL2::[Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex]
* MODEL3::[Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease]
* MODEL4::[Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia]

* MODEL1::[Meta-Analysis of Uci_Death ~ Macrovascular disease (unadjusted)]
* MODEL2::[Meta-Analysis of Uci_Death ~ Macrovascular disease + Age + Sex]
* MODEL3::[Meta-Analysis of Uci_Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease]
* MODEL4::[Meta-Analysis of Uci_Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia]


* MODEL1::[Meta-Analysis of IMV ~ Macrovascular disease (unadjusted)]
* MODEL2::[Meta-Analysis of IMV ~ Macrovascular disease + Age + Sex]
* MODEL3::[Meta-Analysis of IMV ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease]
* MODEL4::[Meta-Analysis of IMV ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia]




**Pending**

* Error checking and debugging 

# Analysis

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, include=F,size="huge")
packages <-c("metafor","esc","readxl","esc","dummies")

ipak<-function(pkg){
  new.pkg<-pkg[!(pkg%in%installed.packages()[,"Package"])]
  if (length(new.pkg))
    install.packages(new.pkg,dependencies=TRUE)
  sapply(pkg,require, character.only=TRUE)}

ipak(packages)

library("meta") 
library("dplyr")
library("ggplot2")

#library("metafor")
#library("esc")
#library("dummies")

# Funcions 
link_source<-paste0("https://github.com/jrealgatius/Stat_codis/blob/master/funcions_propies.R","?raw=T")
devtools::source_url(link_source)


conductor<-here::here("conductor_meta_analisi.xlsx")

conductor_codis2<-here::here("codis_Covid_Agrupadores_juny.xlsx")


# apunts per entendre bé el META_ANALYSIS::

#https://www.rdocumentation.org/packages/meta/versions/1.1-2/topics/forest
#https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/

```

## 1  	Table of Meta-Analysis


```{r lectura, include = TRUE}

base_dades<-readxl::read_excel(conductor)


base_dades<-base_dades %>% select(COUNTRY=camp,LOG_OR=LOG,SE_OR=SE,OR_MACRO,I1,I2)

base_dades%>%
  kable(caption="Table of Meta-Analysis",digits = 2)%>% 
      kableExtra::kable_classic_2(full_width = F)


esquema<-readxl::read_excel(conductor,sheet="esquema")



esquema%>%
  kable(caption="Table of Models",digits = 2)%>% 
      kableExtra::kable_classic_2(full_width = F)



base_dades$LOG_OR<-as.numeric(base_dades$LOG_OR)
base_dades$SE_OR<-as.numeric(base_dades$SE_OR)







```
## 2 Theory:What Are Meta-Analyses?

*Meta-analyses aim to combine results from previous studies in a quantitative way. The goal of meta-analyses is to integrate quantitative outcomes reported in the selected studies into one numerical estimate. This estimate then summarizes all the individual results. Meta-analyses quantify, for example, the effect of a medication, the prevalence of a disease, or the correlation between two properties, across all studies. They can therefore only be applied to studies which report quantitative results. Compared to systematic reviews, meta-analyses often have to be more exclusive concerning the kind of evidence that is summarized. To perform a meta-analysis, it is usually necessary that studies used the same design and type of measurement, and/or delivered the same intervention.* 

**The Statistics I2 (Higgins & Thompson’s Statistic) and τ2 , tell us if there is a lot of variability (Heterogeneity) between the different studies of the Meta-analysis, or if the difference is only due to chance**   

**When the I2, exceeds 25%, or the P of τ2 <0.05, the variability must be studied.*

* I2= 25%: Low heterogeneity
* I2= 50%: Moderate heterogeneity
* I2= 75%: Substantial heterogeneity.

```{r recodes,include=TRUE}

ROR_covid1<-base_dades%>%filter(COUNTRY=="UK_MOD1"       | COUNTRY=="FRANCE_MOD1"   | COUNTRY=="HM_MOD1"  | COUNTRY=="BCN_MOD1" )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid2<-base_dades%>%filter(COUNTRY=="UK_MOD2"       | COUNTRY=="FRANCE_MOD2"   | COUNTRY=="HM_MOD2"  | COUNTRY=="BCN_MOD2" )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid3<-base_dades%>%filter(COUNTRY=="FRANCE_MOD3"   | COUNTRY=="HM_MOD3"       | COUNTRY=="BCN_MOD3" )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid4<-base_dades%>%filter(COUNTRY=="UK_MOD4"       | COUNTRY=="FRANCE_MOD4"   | COUNTRY=="BCN_MOD4" )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid5<-base_dades%>%filter(COUNTRY=="UK_MOD4"       | COUNTRY=="FRANCE_MOD4"   | COUNTRY=="BCN_MOD4" | COUNTRY=="HM_MOD3"   )%>%
  select(COUNTRY,LOG_OR,SE_OR)

ROR_covid1_uci<-base_dades%>%filter(COUNTRY=="UK_MOD1_uci"       | COUNTRY=="FRANCE_MOD1_uci"   | COUNTRY=="HM_MOD1_uci"  | COUNTRY=="BCN_MOD1_uci" )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid2_uci<-base_dades%>%filter(COUNTRY=="UK_MOD2_uci"       | COUNTRY=="FRANCE_MOD2_uci"   | COUNTRY=="HM_MOD2_uci"  | COUNTRY=="BCN_MOD2_uci" )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid3_uci<-base_dades%>%filter(COUNTRY=="FRANCE_MOD3_uci"   | COUNTRY=="HM_MOD3_uci"       | COUNTRY=="BCN_MOD3_uci" )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid4_uci<-base_dades%>%filter(COUNTRY=="UK_MOD4_uci"       | COUNTRY=="FRANCE_MOD4_uci"   | COUNTRY=="BCN_MOD4_uci" )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid5_uci<-base_dades%>%filter(COUNTRY=="UK_MOD4_uci"       | COUNTRY=="FRANCE_MOD4_uci"   | COUNTRY=="BCN_MOD4_uci" | COUNTRY=="HM_MOD3_uci"   )%>%
  select(COUNTRY,LOG_OR,SE_OR)

ROR_covid1_uci_death<-base_dades%>%filter(COUNTRY=="UK_MOD1_uci_death"       | COUNTRY=="FRANCE_MOD1_uci_death"   | COUNTRY=="HM_MOD1_uci_death"   )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid2_uci_death<-base_dades%>%filter(COUNTRY=="UK_MOD2_uci_death"       | COUNTRY=="FRANCE_MOD2_uci_death"   | COUNTRY=="HM_MOD2_uci_death"   )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid3_uci_death<-base_dades%>%filter(COUNTRY=="FRANCE_MOD3_uci_death"   | COUNTRY=="HM_MOD3_uci_death"        )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid4_uci_death<-base_dades%>%filter(COUNTRY=="UK_MOD4_uci_death"       | COUNTRY=="FRANCE_MOD4_uci_death"    )%>%
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid5_uci_death<-base_dades%>%filter(COUNTRY=="UK_MOD4_uci_death"       | COUNTRY=="FRANCE_MOD4_uci_death"   | COUNTRY=="HM_MOD3_uci_death"   )%>%
  select(COUNTRY,LOG_OR,SE_OR)


#11.07.2022#


ROR_covid1_imv<-base_dades%>%filter(COUNTRY=="FRANCE_MOD1_imv")%>% 
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid2_imv<-base_dades%>%filter(COUNTRY=="FRANCE_MOD2_imv")%>% 
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid3_imv<-base_dades%>%filter(COUNTRY=="FRANCE_MOD3_imv")%>% 
  select(COUNTRY,LOG_OR,SE_OR)
ROR_covid4_imv<-base_dades%>%filter(COUNTRY=="FRANCE_MOD4_imv")%>% 
  select(COUNTRY,LOG_OR,SE_OR)
 



```
## 3  	RESULTS:

* Meta-Analysis of Death ~ Macrovascular disease (unadjusted).
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex.
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease.
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.

* Meta-Analysis of Uci ~ Macrovascular disease (unadjusted).
* Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex.
* Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease.
* Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.

* Meta-Analysis of Uci_Death ~ Macrovascular disease (unadjusted).
* Meta-Analysis of Uci_Death ~ Macrovascular disease + Age + Sex.
* Meta-Analysis of Uci_Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease.
* Meta-Analysis of Uci_Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.


```


```
## 3.1  	Meta-Analysis of Death ~ Macrovascular disease (unadjusted).

* UK.Model        Death ~ Macrovascular disease (unadjusted).
* FRANCE.Model    Death ~ Macrovascular disease (unadjusted).
* HM.Model        Death ~ Macrovascular disease (unadjusted).
* BCN.Model       Death ~ Macrovascular disease (unadjusted).


* UK.Model        Uci ~ Macrovascular disease (unadjusted).
* FRANCE.Model    Uci ~ Macrovascular disease (unadjusted).
* HM.Model        Uci ~ Macrovascular disease (unadjusted).
* BCN.Model       Uci ~ Macrovascular disease (unadjusted).


* UK.Model        Uci or death ~ Macrovascular disease (unadjusted).
* FRANCE.Model    Uci or death ~ Macrovascular disease (unadjusted).
* HM.Model        Uci or death ~ Macrovascular disease (unadjusted).


## Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 4 studies (Common effect model).
```{r analisis_1a,include=TRUE}

meta1<-meta::metagen(TE=ROR_covid1$LOG_OR,
               seTE=ROR_covid1$SE_OR,
               studlab = ROR_covid1$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")

meta::forest(meta1,fontsize=8.2, boxsize=5)

```


## Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19).
* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 4 studies (Random effect model).
```{r analisis_1b,include=TRUE}



meta1b<-meta::metagen(TE=ROR_covid1_uci$LOG_OR,
               seTE=ROR_covid1_uci$SE_OR,
               studlab = ROR_covid1_uci$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta1b,fontsize=8.2, boxsize=5)


```

## Meta_Analisi Associations of macrovascular complications with Uci or death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 3 studies, so we will accept the average effect of the 3 studies (Random effect model).
```{r analisis_1c,include=TRUE}




meta1c<-meta::metagen(TE=ROR_covid1_uci_death$LOG_OR,
               seTE=ROR_covid1_uci_death$SE_OR,
               studlab = ROR_covid1_uci_death$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci or death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta1c,fontsize=8.2, boxsize=5)


```


## Meta_Analisi Associations of macrovascular complications with imv in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* 
```{r analisis_1d,include=TRUE}

meta1d<-meta::metagen(TE=ROR_covid1_imv$LOG_OR,
               seTE=ROR_covid1_imv$SE_OR,
               studlab = ROR_covid1_imv$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with imv in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta1d,fontsize=8.2, boxsize=5)


```


## 3.2  	Meta-Analysis of Death ~ Macrovascular disease + Age + Sex.

* UK.Model        Death ~ Macrovascular disease + Age + Sex.
* FRANCE.Model    Death ~ Macrovascular disease + Age + Sex.
* HM.Model        Death ~ Macrovascular disease + Age + Sex.
* BCN.Model       Death ~ Macrovascular disease + Age + Sex.

* UK.Model        Uci ~ Macrovascular disease + Age + Sex.
* FRANCE.Model    Uci ~ Macrovascular disease + Age + Sex.
* HM.Model        Uci ~ Macrovascular disease + Age + Sex.
* BCN.Model       Uci ~ Macrovascular disease + Age + Sex.

* UK.Model        Uci or death ~ Macrovascular disease + Age + Sex.
* FRANCE.Model    Uci or death ~ Macrovascular disease + Age + Sex.
* HM.Model        Uci or death ~ Macrovascular disease + Age + Sex.




## Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 4 studies (Random effect model).
```{r analisis2a,include=TRUE}

meta2<-meta::metagen(TE=ROR_covid2$LOG_OR,
               seTE=ROR_covid2$SE_OR,
               studlab = ROR_covid2$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")

meta::forest(meta2,fontsize=8.2, boxsize=5)






```

## Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 4 studies (Common effect model).
```{r analisis2b,include=TRUE}




meta2b<-meta::metagen(TE=ROR_covid2_uci$LOG_OR,
               seTE=ROR_covid2_uci$SE_OR,
               studlab = ROR_covid2_uci$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta2b,fontsize=8.2, boxsize=5)






```
## Meta_Analisi Associations of macrovascular complications with Uci or death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 3 studies, so we will accept the average effect of the 3 studies (Random effect model).
```{r analisis2c,include=TRUE}



meta2c<-meta::metagen(TE=ROR_covid2_uci_death$LOG_OR,
               seTE=ROR_covid2_uci_death$SE_OR,
               studlab = ROR_covid2_uci_death$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci or death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta2c,fontsize=8.2, boxsize=5)








```


## Meta_Analisi Associations of macrovascular complications with imv in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* ??
```{r analisis2c,include=TRUE}



meta2d<-meta::metagen(TE=ROR_covid2_imv$LOG_OR,
               seTE=ROR_covid2_imv$SE_OR,
               studlab = ROR_covid2_imv$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with imv in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta2d,fontsize=8.2, boxsize=5)








```

## 3.3  	Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease.

* FRANCE.Model    Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes  + Microvascular disease..
* HM.Model        Death ~ Macrovascular disease + Age + Sex + Hypertension + "--------------"  + Microvascular disease.
* BCN.Model       Death ~ Macrovascular disease + Age + Sex + Hypertension + "--------------" + "---------------------"

* FRANCE.Model    Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes  + Microvascular disease..
* HM.Model        Uci ~ Macrovascular disease + Age + Sex + Hypertension + "--------------"  + Microvascular disease.
* BCN.Model       Uci ~ Macrovascular disease + Age + Sex + Hypertension + "--------------" + "---------------------"

* FRANCE.Model    Uci or death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes  + Microvascular disease..
* HM.Model        Uci or death ~ Macrovascular disease + Age + Sex + Hypertension + "--------------"  + Microvascular disease.


## Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 3 studies (Random effect model).

```{r analisis3a,include=TRUE}

meta3<-meta::metagen(TE=ROR_covid3$LOG_OR,
               seTE=ROR_covid3$SE_OR,
               studlab = ROR_covid3$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta3,fontsize=8.2, boxsize=5)



```

## Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 3 studies, so we will accept the average effect of the 3 studies (Common effect model).

```{r analisis3b,include=TRUE}



meta3b<-meta::metagen(TE=ROR_covid3_uci$LOG_OR,
               seTE=ROR_covid3_uci$SE_OR,
               studlab = ROR_covid3_uci$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta3b,fontsize=8.2, boxsize=5)

```

## Meta_Analisi Associations of macrovascular complications with Uci or death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 2 studies, so we will accept the average effect of the 2 studies (Common effect model).


```{r analisis3c,include=TRUE}

meta3c<-meta::metagen(TE=ROR_covid3_uci_death$LOG_OR,
               seTE=ROR_covid3_uci_death$SE_OR,
               studlab = ROR_covid3_uci_death$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci or death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta3c,fontsize=8.2, boxsize=5)



```
## Meta_Analisi Associations of macrovascular complications with imv in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* ???


```{r analisis3d,include=TRUE}

meta3d<-meta::metagen(TE=ROR_covid3_imv$LOG_OR,
               seTE=ROR_covid3_imv$SE_OR,
               studlab = ROR_covid3_imv$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with imv in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta3d,fontsize=8.2, boxsize=5)



```



## 3.4  	Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease+BMI + Etnia.

* UK.Model        Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* FRANCE.Model    Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* BCN.Model       Death ~ Macrovascular disease + Age + Sex + "-----------"+ "--------------" + Microvascular disease + BMI + Etnia.

* UK.Model        Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* FRANCE.Model    Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* BCN.Model       Uci ~ Macrovascular disease + Age + Sex + "-----------"+ "--------------" + Microvascular disease + BMI + Etnia.

* UK.Model        Uci or death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* FRANCE.Model    Uci or death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.



## Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 3 studies, so we will accept the average effect of the 3 studies (Common effect model).

```{r analisis4a,include=TRUE}


meta4<-meta::metagen(TE=ROR_covid4$LOG_OR,
               seTE=ROR_covid4$SE_OR,
               studlab = ROR_covid4$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")

meta::forest(meta4,fontsize=8.2, boxsize=5)


```

## Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 3 studies, so we will accept the average effect of the 3 studies (Common effect model).

```{r analisis4b,include=TRUE}


meta4b<-meta::metagen(TE=ROR_covid4_uci$LOG_OR,
               seTE=ROR_covid4_uci$SE_OR,
               studlab = ROR_covid4_uci$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta4b,fontsize=8.2, boxsize=5)


```

## Meta_Analisi Associations of macrovascular complications with Uci or death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 2 studies, so we will accept the average effect of the 2 studies (Random effect model).

```{r analisis4c,include=TRUE}


meta4c<-meta::metagen(TE=ROR_covid4_uci_death$LOG_OR,
               seTE=ROR_covid4_uci_death$SE_OR,
               studlab = ROR_covid4_uci_death$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci or death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta4c,fontsize=8.2, boxsize=5)



```
## Meta_Analisi Associations of macrovascular complications with imv in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* ???

```{r analisis4d,include=TRUE}


meta4d<-meta::metagen(TE=ROR_covid4_imv$LOG_OR,
               seTE=ROR_covid4_imv$SE_OR,
               studlab = ROR_covid4_imv$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with imv in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta4d,fontsize=8.2, boxsize=5)



```


## 3.5  	Meta-Analysis of General.

* UK.Model        Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* FRANCE.Model    Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* HM.Model        Death ~ Macrovascular disease + Age + Sex + Hypertension + "--------------"  + Microvascular disease.
* BCN.Model       Death ~ Macrovascular disease + Age + Sex + "-----------"+ "--------------" + Microvascular disease + BMI + Etnia.

* UK.Model        Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* FRANCE.Model    Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* HM.Model        Uci ~ Macrovascular disease + Age + Sex + Hypertension + "--------------"  + Microvascular disease.
* BCN.Model       Uci ~ Macrovascular disease + Age + Sex + "-----------"+ "--------------" + Microvascular disease + BMI + Etnia.

* UK.Model        Uci or death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* FRANCE.Model    Uci or death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* HM.Model        Uci or death ~ Macrovascular disease + Age + Sex + Hypertension + "--------------"  + Microvascular disease.





## Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 4 studies (Common effect model).


```{r analisis5a,include=TRUE}

meta5<-meta::metagen(TE=ROR_covid5$LOG_OR,
               seTE=ROR_covid5$SE_OR,
               studlab = ROR_covid5$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta5,fontsize=8.2, boxsize=5)



```

## Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 4 studies (Common effect model).

```{r analisis5b,include=TRUE}






meta5b<-meta::metagen(TE=ROR_covid5_uci$LOG_OR,
               seTE=ROR_covid5_uci$SE_OR,
               studlab = ROR_covid5_uci$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta5b,fontsize=8.2, boxsize=5)




```


## Meta_Analisi Associations of macrovascular complications with Uci or death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)
* In this  case, there is  not variability between the 3 studies, so we will accept the average effect of the 3 studies (Random effect model).


```{r analisis5c,include=TRUE}

meta5c<-meta::metagen(TE=ROR_covid5_uci_death$LOG_OR,
               seTE=ROR_covid5_uci_death$SE_OR,
               studlab = ROR_covid5_uci_death$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci or death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta5c,fontsize=8.2, boxsize=5)


```







## 4. ANNEX: Macrovascular Complications Codes 


```{r codis_MACRO, include=T}


readxl::read_excel(conductor_codis2,col_types = "text")%>%dplyr::select(cod,Descripcio,agr,agr0,agr2)%>%mutate(K="==")%>% filter(agr0=="MACR")%>%dplyr::select(cod,agr0,agr,K,Descripcio)%>% knitr::kable(caption="ICD10 Macrovascular Complications Codes ")



```


# References


---
nocite: '@*'
...




&nbsp;
<hr />
<p style="text-align: center;">A work by $Jordi Real$ $Rai Puig$ </a></p>
<p style="text-align: center;">$Llepali System$ </a></p>
<p style="text-align: center;"><span style="color: #808080;"><em><https://github.com/USR-DAPCAT/></em></span></p>


