---
title: "Meta_Analisi.Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19). \\pkg{foo}"
author: "Rai Puig & Jordi Real"
website: "https://github.com/USR-DAPCAT/"

date: "`r format(Sys.time(), '%d %B, %Y')`"


output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    fig_caption: true
    css: logos_css/usr_styles.css
  pdf_document: default
  word_document: default

---

&nbsp;
<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<img src=\"https://www.idiapjgol.org/images/logo.png\" style=\"float: right ;width: 130px;\"/>')
     $head.prepend('<img src=\"https://avatars2.githubusercontent.com/u/57066591?s=200&v=4\" style=\"margin-left:25% ;width: 80px;\"/>')
     $head.prepend('<img src=\"logos_css/logoDAP_Cat.png\" style=\"float: left:1;width: 185px;\"/>')
   });
</script>


<div class="watermark">DRAFT</div>

****



# 0. State:

**Latest updates** 

> February/2022

**Done**

* Meta_Analisi Associations of macrovascular complications DM and Covid-19: UK,France,HM(Spain),Barcelona
* Meta-Analysis of Death ~ Macrovascular disease (unadjusted).
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex.
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease. 
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.

**Pending**

* Error checking and debugging 

# Analysis

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, include=F,size="huge")
packages <-c("metafor","esc","readxl","esc","dummies")

ipak<-function(pkg){
  new.pkg<-pkg[!(pkg%in%installed.packages()[,"Package"])]
  if (length(new.pkg))
    install.packages(new.pkg,dependencies=TRUE)
  sapply(pkg,require, character.only=TRUE)}

ipak(packages)

library("meta") 
library("dplyr")
library("ggplot2")

#library("metafor")
#library("esc")
#library("dummies")

# Funcions 
link_source<-paste0("https://github.com/jrealgatius/Stat_codis/blob/master/funcions_propies.R","?raw=T")
devtools::source_url(link_source)


conductor<-here::here("conductor_meta_analisi.xlsx")


# apunts per entendre bé el META_ANALYSIS::

#https://www.rdocumentation.org/packages/meta/versions/1.1-2/topics/forest
#https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/

```

## 1  	Table of Meta-Analysis


```{r lectura, include = TRUE}

base_dades<-readxl::read_excel(conductor)


base_dades<-base_dades %>% select(COUNTRY=camp,LOG_OR=LOG,SE_OR=SE,OR_MACRO,I1,I2)

base_dades%>%
  kable(caption="Table of Meta-Analysis",digits = 2)%>% 
      kableExtra::kable_classic_2(full_width = F)



base_dades$LOG_OR<-as.numeric(base_dades$LOG_OR)
base_dades$SE_OR<-as.numeric(base_dades$SE_OR)



```
## 2 Theory:What Are Meta-Analyses?

*Meta-analyses aim to combine results from previous studies in a quantitative way. The goal of meta-analyses is to integrate quantitative outcomes reported in the selected studies into one numerical estimate. This estimate then summarizes all the individual results. Meta-analyses quantify, for example, the effect of a medication, the prevalence of a disease, or the correlation between two properties, across all studies. They can therefore only be applied to studies which report quantitative results. Compared to systematic reviews, meta-analyses often have to be more exclusive concerning the kind of evidence that is summarized. To perform a meta-analysis, it is usually necessary that studies used the same design and type of measurement, and/or delivered the same intervention.* 

**The Statistics I2 (Higgins & Thompson’s Statistic) and τ2 , tell us if there is a lot of variability (Heterogeneity) between the different studies of the Meta-analysis, or if the difference is only due to chance**   

**When the I2, exceeds 25%, or the P of τ2 <0.05, the variability must be studied.*

* I2= 25%: Low heterogeneity
* I2= 50%: Moderate heterogeneity
* I2= 75%: Substantial heterogeneity.

```{r recodes,include=TRUE}


ROR_covid1<-base_dades%>%filter(COUNTRY=="UK_MOD1"       | COUNTRY=="FRANCE_MOD1"   | COUNTRY=="HM_MOD1"  | COUNTRY=="BCN_MOD1" )%>%select(COUNTRY,LOG_OR,SE_OR)
ROR_covid2<-base_dades%>%filter(COUNTRY=="UK_MOD2"       | COUNTRY=="FRANCE_MOD2"   | COUNTRY=="HM_MOD2"  | COUNTRY=="BCN_MOD2" )%>%select(COUNTRY,LOG_OR,SE_OR)
ROR_covid3<-base_dades%>%filter(COUNTRY=="FRANCE_MOD3"   | COUNTRY=="HM_MOD3"       | COUNTRY=="BCN_MOD3" )%>%select(COUNTRY,LOG_OR,SE_OR)
ROR_covid4<-base_dades%>%filter(COUNTRY=="UK_MOD4"       | COUNTRY=="FRANCE_MOD4"   | COUNTRY=="BCN_MOD4" )%>%select(COUNTRY,LOG_OR,SE_OR)
```
## 3  	RESULTS:

* Meta-Analysis of Death ~ Macrovascular disease (unadjusted).
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex.
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease.
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.

```{r analisis0,include=TRUE}



```

## 3.1  	Meta-Analysis of Death ~ Macrovascular disease (unadjusted).

* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 4 studies (Common effect model).

```{r analisis1,include=TRUE}

#1# .	Death ~ Macrovascular disease (unadjusted)

meta1<-meta::metagen(TE=ROR_covid1$LOG_OR,
               seTE=ROR_covid1$SE_OR,
               studlab = ROR_covid1$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta1,fontsize=8.2, boxsize=5)



```

## 3.2  	Meta-Analysis of Death ~ Macrovascular disease + Age + Sex.

* In this  case, there is  variability between the 4 studies, so we will accept the average effect of the 4 studies (Random effect model).

```{r analisis2,include=TRUE}

#2# .	Death ~ Macrovascular disease + Age + Sex


meta2<-meta::metagen(TE=ROR_covid2$LOG_OR,
               seTE=ROR_covid2$SE_OR,
               studlab = ROR_covid2$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta2,fontsize=8.2, boxsize=5)


```

## 3.3  	Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease.

* In this  case, there is  variability between the 4 studies, so we will accept the average effect of the 4 studies (Random effect model).

```{r analisis3,include=TRUE}

#3# .	Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease 


meta3<-meta::metagen(TE=ROR_covid3$LOG_OR,
               seTE=ROR_covid3$SE_OR,
               studlab = ROR_covid3$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta3,fontsize=8.2, boxsize=5)



```

## 3.4  	Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease+BMI + Etnia.

* In this  case, there is  not variability between the 3 studies, so we will accept the average effect of the 3 studies (Common effect model).

```{r analisis4,include=TRUE}

#



meta4<-meta::metagen(TE=ROR_covid4$LOG_OR,
               seTE=ROR_covid4$SE_OR,
               studlab = ROR_covid4$COUNTRY,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta4,fontsize=8.2, boxsize=5)




```



```



&nbsp;
<hr />
<p style="text-align: center;">A work by $Jordi Real$ $Rai Puig$ </a></p>
<p style="text-align: center;">$Llepali System$ </a></p>
<p style="text-align: center;"><span style="color: #808080;"><em><https://github.com/USR-DAPCAT/></em></span></p>


