---
title: "Meta_Analisi.Associations of macrovascular complications(Peripheral Vascular Disease-PVD) with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19). \\pkg{foo}"
author: "Rai Puig & Jordi Real"
website: "https://github.com/USR-DAPCAT/"

date: "`r format(Sys.time(), '%d %B, %Y')`"


output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    fig_caption: true
    css: logos_css/usr_styles.css
  pdf_document: default
  word_document: default
  
  bibliography: references.bib 
---

&nbsp;
<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<img src=\"https://www.idiapjgol.org/images/logo.png\" style=\"float: right ;width: 130px;\"/>')
     $head.prepend('<img src=\"https://avatars2.githubusercontent.com/u/57066591?s=200&v=4\" style=\"margin-left:25% ;width: 80px;\"/>')
     $head.prepend('<img src=\"logos_css/logoDAP_Cat.png\" style=\"float: left:1;width: 185px;\"/>')
   });
</script>


<div class="watermark">DRAFT</div>

****



# 0. State:

**Latest updates** 

> July/2022

**Done**

* Meta_Analisi Associations of macrovascular(PVD) complications DM and Covid-19: UK,France,HM(Spain),Barcelona

* MODEL1::[Meta-Analysis of Death ~ Macrovascular disease (unadjusted)]
* MODEL2::[Meta-Analysis of Death ~ Macrovascular disease + Age + Sex]
* MODEL3::[Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease] 


* MODEL1::[Meta-Analysis of Uci ~ Macrovascular disease (unadjusted)]
* MODEL2::[Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex]
* MODEL3::[Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease]


* MODEL1::[Meta-Analysis of Imv ~ Macrovascular disease (unadjusted)]
* MODEL2::[Meta-Analysis of Imv ~ Macrovascular disease + Age + Sex]
* MODEL3::[Meta-Analysis of Imv ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease]





**Pending**

* Error checking and debugging 

# Analysis

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, include=F,size="huge")
packages <-c("metafor","esc","readxl","esc","dummies")

ipak<-function(pkg){
  new.pkg<-pkg[!(pkg%in%installed.packages()[,"Package"])]
  if (length(new.pkg))
    install.packages(new.pkg,dependencies=TRUE)
  sapply(pkg,require, character.only=TRUE)}

ipak(packages)

library("meta") 
library("dplyr")
library("ggplot2")

#library("metafor")
#library("esc")
#library("dummies")

# Funcions 
link_source<-paste0("https://github.com/jrealgatius/Stat_codis/blob/master/funcions_propies.R","?raw=T")
devtools::source_url(link_source)


conductor<-here::here("conductor_meta_analisi.xlsx")

conductor_codis2<-here::here("codis_Covid_Agrupadores_juny.xlsx")


# apunts per entendre bé el META_ANALYSIS::

#https://www.rdocumentation.org/packages/meta/versions/1.1-2/topics/forest
#https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/

```

## 1  	Table of Meta-Analysis


```{r lectura, include = TRUE}

base_dades<-readxl::read_excel(conductor,sheet = "base_dades_PVD")


base_dades<-base_dades %>% select(COUNTRY=camp,COUNTRY2=camp2,LOG_OR=LOG,SE_OR=SE,OR_MACRO,I1,I2)

base_dades%>%
  kable(caption="Table of Meta-Analysis",digits = 2)%>% 
      kableExtra::kable_classic_2(full_width = F)


#esquema<-readxl::read_excel(conductor,sheet="esquema")



#esquema%>%
#  kable(caption="Table of Models",digits = 2)%>% 
#      kableExtra::kable_classic_2(full_width = F)



base_dades$LOG_OR<-as.numeric(base_dades$LOG_OR)
base_dades$SE_OR<-as.numeric(base_dades$SE_OR)







```
# 1.2 Flow Chart


```{r flow_Chart,include=TRUE, warning=F}

Flow_chart_Consort<-function(dt=ggconsort::trial_data,
                             exclusions=c("declined","prior_chemo","bone_mets"),
                             sequencial=TRUE,
                             grups=NA,
                             lab_start="Assessed for eligibility",
                             lab_random="Analyzed sample",
                             lab_exclusions=NULL)
{

  ## Testing
  # dt=dt_nova
  # exclusions= exclusions
  # lab_exclusions=variables$labels
  # grups = grups
  # sequencial=sequencial
  # lab_start="Assessed for eligibility"
  # lab_random="Randomized"
  # lab_exclusions=NULL

  # dt=trial_data
  # exclusions=c("declined","prior_chemo","bone_mets")
  # # # Parametres
  # lab_start="Assessed for eligibility"
  # lab_random="Randomized"
  # lab_exclusions=c("A","B","C")
  # dt=trial_data
  # exclusions<-c("exclusio1", "exclusio2","exclusio3")
  # exclusions=c("declined","prior_chemo","bone_mets")
  # exclusions=c("prior_chemo","bone_mets")
  # # exclusions=c("bone_mets")
  # grups="treatment"
  # sequencial=T
  # grups=NA
  # grups="treatment"
  # # #
  # # #
  # dt=iris
  # exclusions=c("Sepal.Length < 5","Species=='setosa'")

  # Proces per dicotomitzar criteris d'inclusió
  # vector_crit_excl<-c("DG.ANGOR","edat<30 | edat>=90","ANT.FA","ANT.event","sexe=='H'","DG.AIT")
  # subvector_a_canviar<-vector_crit_excl[vector_crit_excl %in% (dt_temp %>% names())] %>% paste0("==1")
  # vector_crit_excl[vector_crit_excl %in% (dt_temp %>% names())]<-subvector_a_canviar

  # Dicotomitzar....
  subvector_a_canviar<-exclusions[exclusions %in% (dt %>% names())] %>% paste0("==1")
  exclusions[exclusions %in% (dt %>% names())]<-subvector_a_canviar
  dt<-generar_dummies_exclusions(dt=dt, criteris=exclusions)

  # Num d'exclusions
  N_exc<-length(exclusions)
  noms_exclusions<-exclusions
  exclusions<-paste0("exclusio",c(1:N_exc))

  # Selecciono camps necessaris de dt (dades)
  if (is.na(grups))
  {dt<-dt %>%
    dplyr::select(exclusions) %>% dplyr::mutate(grup="Overall",idp = row_number())
  grup<-"Overall"} else
  {dt<-dt %>% dplyr::select(exclusions,grup=grups) %>% dplyr::mutate(idp = dplyr::row_number())}

  # capturar etiquetes
  if (is.null(lab_exclusions)) labels_exclusions<-noms_exclusions else labels_exclusions<-lab_exclusions

  label_grup<-grups
  levels_grup<-dt %>% dplyr::select(grup) %>% stats::na.omit() %>% dplyr::distinct() %>% dplyr::pull(grup)
  # Canvi de categories a grup numerats en character
  dt<-dt %>% dplyr::mutate(grup=as.factor(grup) %>% as.numeric(),
                           grup=dplyr::if_else(!is.na(grup),as.character(paste0("grup",grup)),NA_character_))

  # Generar dataframes de filtre

  # Inclusions sequencials
  # Genero fitxers inclusions sequencials
  dtlist_incl<-seq(1:N_exc) %>%
    purrr::map(~paste0("!",exclusions[1:.x],collapse = " & ")) %>%
    purrr::map(~dt %>% dplyr::filter(eval(parse(text = .x)))) %>%
    purrr::set_names(paste0("included",1:N_exc))

  # Inclusio final
  dt_inclusio_final<-dtlist_incl[N_exc] %>% purrr::set_names("Included_final")

  # Generar fitxers d'exclusions sequencials
  dt_excluded_totals = dplyr::anti_join(dt, dt_inclusio_final[[1]], by = "idp")
  dt_exc1 = dplyr::anti_join(dt, dtlist_incl[[1]], by = "idp")
  # si hi ha una unica exclusio dtlist_exclusions<-NULL

  if (N_exc>1) {
    if (sequencial) {
      dtlist_exclusions<-
        purrr::map2(dtlist_incl[1:(N_exc-1)],dtlist_incl[-1],~anti_join(.x,.y,by = "idp")) %>%
        purrr::set_names(paste0("Excluded",c(2:N_exc)))} else {

          dtlist_exclusions<-c(2:N_exc) %>%
            purrr::map(~paste0(exclusions[.x],"==1")) %>%
            purrr::map(~dt %>% dplyr::filter(eval(parse(text = .x)))) %>%
            purrr::set_names(paste0("Excluded",2:N_exc))
        }} else {dtlist_exclusions<-NULL}

  dtlist_exclusions<-append(list(Excluded1=dt_exc1),dtlist_exclusions)
  # Inclusions finals per grups
  # grup="FF.HTA"
  dt_inclusions_grups<-
    dtlist_incl[[N_exc]] %>% base::split(.[["grup"]])

  # # Elimino els NA's
  # dt_inclusions_grups$grupNA<-NULL

  # Fusionar llistats de de inclosos + exclosos
  llistat_arguments<-
    c(dt_inclusio_final,dtlist_incl,dt_inclusions_grups,
      list(Excluded_total=dt_excluded_totals),
      dtlist_exclusions)

  arglist = append(list(cohort_start(dt,lab_start)),
                   llistat_arguments)

  # Generar les cohorts via funció
  dades_cohorts<-
    do.call(cohort_define,
            arglist)

  # Provide text labels for cohorts ---------------------------
  llistat_noms<-dades_cohorts$data %>% names()

  llistat_labels<- c(lab_start,lab_random,
                     paste0("Included",c(1:N_exc)),
                     levels_grup,"Excluded",labels_exclusions)

  # Labels
  # llistat_noms<-dades_cohorts$data %>% names()
  # llistat_noms<-c(".full","Included_final", paste0("Included",c(1:N_exc)),
  #                 paste0("grup",1:length(levels_grup)),
  #                 "Excluded_total",  paste0("Excluded",c(1:N_exc)))

  for (i in 1:length(llistat_noms)) {
    dades_cohorts$labels[llistat_noms[i]]<-llistat_labels[i]}

  study_cohorts<-dades_cohorts

  #
  # study_cohorts<-
  #   dades_cohorts %>%
  #   cohort_label(
  #     Included_final = lab_random,
  #     grup1= "Allocated to arm A",
  #     grup2 = "Allocated to arm B",
  #     Excluded_total = "Excluded",
  #     Excluded1 = "Declined to participate",
  #     Excluded2 = "Prior chemotherapy",
  #     Excluded3 = "Bone metastasis")

  # Generar caixa d'exclusions
  noms_exc<-paste0("Excluded",1:N_exc)

  caixa_exc<-noms_exc %>%
    purrr::map_chr(~paste0('• {cohort_count_adorn(study_cohorts, ', .x,')}<br>')) %>%
    glue::glue_collapse()
  caixa_exclusions<-paste0(
    "{cohort_count_adorn(study_cohorts, Excluded_total)}<br>",
    caixa_exc)


  study_consort <- study_cohorts %>%
    ggconsort::consort_box_add(
      "full", 0, 50, ggconsort::cohort_count_adorn(study_cohorts, .full)
    ) %>%
    ggconsort::consort_box_add(
      lab_random, 0, 30, ggconsort::cohort_count_adorn(study_cohorts,Included_final)
    ) %>%

    # consort_box_add(
    #   "exclusions", 20, 40, glue::glue(caixa_exclusions)
    # ) %>%


    ggconsort::consort_box_add(
      "exclusions", 10, 40, glue::glue(caixa_exclusions)
    ) %>%


    ggconsort::consort_arrow_add(
      end = "exclusions", end_side = "left", start_x = 0, start_y = 40
    ) %>%
    ggconsort::consort_arrow_add(
      "full", "bottom", lab_random, "top"
    )

  # En cas de By grups
  if (!is.na(grups)) {

    # By grups
    study_consort <- study_consort %>%

      ggconsort::consort_box_add(
        "arm_a", -30, 10, ggconsort::cohort_count_adorn(study_cohorts, grup1)
      ) %>%

      ggconsort::consort_box_add(
        "arm_b", 30, 10, ggconsort::cohort_count_adorn(study_cohorts, grup2)
      )

    study_consort<- study_consort %>%
      ggconsort::consort_arrow_add(
        start_x = 0, start_y = 30, end_x = 0, end_y = 20,
      ) %>%
      ggconsort::consort_line_add(
        start_x = -30, start_y = 20, end_x = 30, end_y = 20,
      )  %>%
      ggconsort::consort_arrow_add(
        end = "arm_a", end_side = "top", start_x = -30, start_y = 20
      ) %>%
      ggconsort::consort_arrow_add(
        end = "arm_b", end_side = "top", start_x = 30, start_y = 20)

  }

  ## Fer-ho maco


  if (!is.na(grups)) {

    study_consort %>%
      ggplot2::ggplot() +
      ggconsort::geom_consort() +
      ggconsort::theme_consort(margin_h = 8, margin_v = 1) +
      # you can include other ggplot geoms, as needed -------------
    ggtext::geom_richtext(
      aes(x = 0, y = 10, label = "Allocation"),
      fill = "#9bc0fc") } else
      {
        study_consort %>%
          ggplot2::ggplot() +
          ggconsort::geom_consort() + xlim(-10,20) +
          ggconsort::theme_consort(margin_h = 10, margin_v = 1)
      }
}


generar_dummies_exclusions<-function(dt=iris, criteris=c("Sepal.Length < 5","Species=='setosa'")) {

  # dt=dt
  # criteris=exclusions
  # dt=dt, criteris=exclusions

  # Generar dummies segons criteris d'inclusió
  num_excl<-criteris %>% length()
  cols_dummies<-paste0("exclusio",c(1:num_excl))

  dt_dumies<-
    purrr::map2_dfc(criteris,cols_dummies,
                    ~dplyr::transmute(dt,!!sym(.y):=eval(parse(text=.x)))
    ) %>% dplyr::mutate_all(as.numeric)

  # Juntar-ho tot
  # Truc per eliminar dumiis existents en dt
  vars_dt<-names(dt)[!names(dt)%in% c(names(dt_dumies))]
  dt %>% select(vars_dt) %>% dplyr::bind_cols(dt_dumies)

}

criteris_exclusio_ggconsort<-function(dt=dades,taulavariables="VARIABLES_R3b.xls",criteris="exclusio1",missings=T,...) {

  # dt=dades
  # taulavariables=conductor
  # sheet="Exclusions"
  # criteris="exclusio"
  # missings=T


  ##  2. Eliminar els espais en blanc de les variables factors del data.frame
  dt<-dt %>%
    dplyr::mutate_if(is.factor,funs(str_trim(.))) %>%
    dplyr::mutate_if(is.character,funs(str_trim(.)))

  ##  Llegeix criteris de variables
  variables <- read_conductor(taulavariables,col_types = "text",...) %>% tidyr::as_tibble() %>% dplyr::select(camp,!!criteris)
  # variables <- read_conductor(taulavariables,col_types = "text",sheet=sheet) %>% tidyr::as_tibble() %>% dplyr::select(camp,!!criteris)
  # Filtrar valors
  criteris_sym<-sym(criteris)
  variables<-variables %>% dplyr::filter(!is.na(!!criteris_sym))
  # variables[is.na(variables)]<- 0

  # llista de caracters logics del filtre
  char_logics<-c(">",">=","<","<=","==","!=","is.na") %>% paste0(collapse = '|')

  ##  0. Filtro taula variables només variables implicades en el filtre i el genero
  maco<-variables %>%
    dplyr::filter_(paste0(criteris,"!=0")) %>% dplyr::select_("camp",criteris) %>%
    transmute_("camp","crit_temp"=criteris) %>%
    # if criteri missing is.na()
    mutate(crit_temp=if_else(str_detect(crit_temp,"is.na"),paste0("is.na(",camp,")"),crit_temp)) %>%
    mutate(camp=if_else(str_detect(crit_temp,"is.na"),"",camp)) %>%
    # Si es texte sense igualtat --> la poso
    mutate(crit_temp=if_else(str_detect(crit_temp,char_logics),crit_temp,paste0("=='",crit_temp,"'")))

  # Genero la llista de filtres
  maco<-maco %>% mutate(filtres=paste0("(",crit_temp,")"))

  # Afegir valors valids per aplicar criteri (Si missings==F)
  if (missings==F) maco<-maco %>% mutate(filtres=stringr::str_c("(", filtres, " & !is.na(",camp, "))"))

  # Concateno condicions amb un OR
  maco<-str_c(maco$filtres,collapse=" | ")

  ## 1. Genera filtre en base a columna exclusio1   popes
  popes<-str_c("!(",maco,")")

  ##  3. Aplicar filtre: popes a dt
  dt %>% dplyr::filter(eval(parse(text=popes)))

}




#devtools::install_github("jrealgatius/ggflowchart")


UK_POB<-1846 
UK_MIS<-1333
FRANCE_POB<-1510
FRANCE_MIS<-1333
HM_POB<-406
HM_MIS<-0
SPAIN_POB<-344
SPAIN_MIS<-23

Ntotal<-UK_POB+FRANCE_POB+HM_POB+SPAIN_POB
N_missings<-UK_MIS+FRANCE_MIS+HM_MIS+SPAIN_MIS

#N_joves<-100

library(ggconsort)
library(dplyr)

dades<-
  tibble::tibble(id=1:Ntotal,missings=1:Ntotal) %>%
  mutate(missings=if_else(missings<=N_missings,1,0))


Flow_chart_Consort(dt=dades,
                   exclusions=c("missings"),sequencial=TRUE,grups=NA,
                   lab_start="Assessed for eligibility Complete Data for Macrovascular complications",
                   lab_random="Analyzed sample",
                   lab_exclusions="Missings")


```
## 2 Theory:What Are Meta-Analyses?

*Meta-analyses aim to combine results from previous studies in a quantitative way. The goal of meta-analyses is to integrate quantitative outcomes reported in the selected studies into one numerical estimate. This estimate then summarizes all the individual results. Meta-analyses quantify, for example, the effect of a medication, the prevalence of a disease, or the correlation between two properties, across all studies. They can therefore only be applied to studies which report quantitative results. Compared to systematic reviews, meta-analyses often have to be more exclusive concerning the kind of evidence that is summarized. To perform a meta-analysis, it is usually necessary that studies used the same design and type of measurement, and/or delivered the same intervention.* 

**The Statistics I2 (Higgins & Thompson’s Statistic) and τ2 , tell us if there is a lot of variability (Heterogeneity) between the different studies of the Meta-analysis, or if the difference is only due to chance**   

**When the I2, exceeds 25%, or the P of τ2 <0.05, the variability must be studied.*

* I2= 25%: Low heterogeneity
* I2= 50%: Moderate heterogeneity
* I2= 75%: Substantial heterogeneity.

```{r recodes,include=TRUE}

ROR_covid1<-base_dades%>%filter(COUNTRY=="UK_MOD1"       | COUNTRY=="FRANCE_MOD1"   | COUNTRY=="HM_MOD1"  | COUNTRY=="BCN_MOD1" )%>%
  select(COUNTRY2,LOG_OR,SE_OR)
ROR_covid2<-base_dades%>%filter(COUNTRY=="UK_MOD2"       | COUNTRY=="FRANCE_MOD2"   | COUNTRY=="HM_MOD2"  | COUNTRY=="BCN_MOD2" )%>%
  select(COUNTRY2,LOG_OR,SE_OR)
ROR_covid3<-base_dades%>%filter(COUNTRY=="UK_MOD3"       | COUNTRY=="FRANCE_MOD3"   | COUNTRY=="HM_MOD3"  | COUNTRY=="BCN_MOD3" )%>%
  select(COUNTRY2,LOG_OR,SE_OR)
ROR_covid4<-base_dades%>%filter(COUNTRY=="UK_MOD4"       | COUNTRY=="FRANCE_MOD4"  )%>%
  select(COUNTRY2,LOG_OR,SE_OR)



ROR_covid1_uci<-base_dades%>%filter(COUNTRY=="UK_MOD1_uci"       | COUNTRY=="FRANCE_MOD1_uci"   | COUNTRY=="HM_MOD1_uci" )%>%
  select(COUNTRY2,LOG_OR,SE_OR)
ROR_covid2_uci<-base_dades%>%filter(COUNTRY=="UK_MOD2_uci"       | COUNTRY=="FRANCE_MOD2_uci"   | COUNTRY=="HM_MOD2_uci" )%>%
  select(COUNTRY2,LOG_OR,SE_OR)
ROR_covid3_uci<-base_dades%>%filter(COUNTRY=="UK_MOD3_uci"       | COUNTRY=="FRANCE_MOD3_uci"   | COUNTRY=="HM_MOD3_uci" )%>%
  select(COUNTRY2,LOG_OR,SE_OR)
ROR_covid4_uci<-base_dades%>%filter(COUNTRY=="UK_MOD4_uci"        | COUNTRY=="FRANCE_MOD4_uci"  )%>%
  select(COUNTRY2,LOG_OR,SE_OR)




ROR_covid1_imv<-base_dades%>%filter(COUNTRY=="FRANCE_MOD1_imv"  )%>% 
  select(COUNTRY2,LOG_OR,SE_OR)
ROR_covid2_imv<-base_dades%>%filter(COUNTRY=="FRANCE_MOD2_imv"  )%>% 
  select(COUNTRY2,LOG_OR,SE_OR)
ROR_covid3_imv<-base_dades%>%filter(COUNTRY=="FRANCE_MOD3_imv"  )%>% 
  select(COUNTRY2,LOG_OR,SE_OR)
ROR_covid4_imv<-base_dades%>%filter(COUNTRY=="FRANCE_MOD4_imv"  )%>% 
  select(COUNTRY2,LOG_OR,SE_OR)


```
## 3  	RESULTS:

* Meta-Analysis of Death ~ Macrovascular disease (unadjusted).
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex.
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease.
* Meta-Analysis of Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.

* Meta-Analysis of Uci ~ Macrovascular disease (unadjusted).
* Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex.
* Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease.
* Meta-Analysis of Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.



* Meta-Analysis of imv ~ Macrovascular disease (unadjusted).
* Meta-Analysis of imv ~ Macrovascular disease + Age + Sex.
* Meta-Analysis of imv ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease.
* Meta-Analysis of imv ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.


```


```
## 3.1  	Meta-Analysis of Death/Uci/Imv~ Macrovascular disease -PVD- (unadjusted).

* UK.Model        Death ~ Macrovascular disease (unadjusted).
* FRANCE.Model    Death ~ Macrovascular disease (unadjusted).
* HM.Model        Death ~ Macrovascular disease (unadjusted).
* BCN.Model       Death ~ Macrovascular disease (unadjusted).


* UK.Model        Uci ~ Macrovascular disease (unadjusted).
* FRANCE.Model    Uci ~ Macrovascular disease (unadjusted).
* HM.Model        Uci ~ Macrovascular disease (unadjusted).




* FRANCE.Model    imv ~ Macrovascular disease (unadjusted).




## Meta_Analisi Associations of macrovascular complications -PVD- with DEATH in patients with diabetes hospitalized for Coronavirus disease(COVID-19).Unadjusted model
* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 4 studies (Common effect model).
```{r analisis_1a,include=TRUE}

meta1<-meta::metagen(TE=ROR_covid1$LOG_OR,
               seTE=ROR_covid1$SE_OR,
               studlab = ROR_covid1$COUNTRY2,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta1,
             fontsize=9,
             boxsize=5,
             col.square="black", 
             hetstat=TRUE,
             leftcols="studlab",
             rightcols=c("effect","ci","w.fixed"),
             xlim=c(0.2, 5),
             squaresize=0.5,
             print.tau2 = FALSE,
             print.I2= TRUE,
             plotwidth=unit(9,"cm"),
             colgap=unit(3, "mm"))


```


## Meta_Analisi Associations of macrovascular complications -PVD- with UCI in patients with diabetes hospitalized for Coronavirus disease(COVID-19).Unadjusted model
* In this  case, there is  not variability between the 3 studies, so we will accept the average effect of the 3 studies (Common effect model).
```{r analisis_1b,include=TRUE}



meta1b<-meta::metagen(TE=ROR_covid1_uci$LOG_OR,
               seTE=ROR_covid1_uci$SE_OR,
               studlab = ROR_covid1_uci$COUNTRY2,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")



meta::forest(meta1b,
             fontsize=8.2, 
             boxsize=5, 
             col.square="black", 
             hetstat=TRUE,
             leftcols="studlab",
             rightcols=c("effect", "ci","w.fixed"),
             xlim=c(0.1, 5),
             squaresize=0.5,
             plotwidth=unit(9, "cm"),
             colgap=unit(3, "mm"))


```





## 3.2  	Meta-Analysis of Death/Uci/Uci_Death/Imv ~ Macrovascular -PVD- disease + Age + Sex.

* UK.Model        Death ~ Macrovascular disease + Age + Sex.
* FRANCE.Model    Death ~ Macrovascular disease + Age + Sex.
* HM.Model        Death ~ Macrovascular disease + Age + Sex.
* BCN.Model       Death ~ Macrovascular disease + Age + Sex.

* UK.Model        Uci ~ Macrovascular disease + Age + Sex.
* FRANCE.Model    Uci ~ Macrovascular disease + Age + Sex.
* HM.Model        Uci ~ Macrovascular disease + Age + Sex.

* FRANCE.Model    imv ~ Macrovascular disease + Age + Sex.



## Meta_Analisi Associations of macrovascular complications -PVD- with DEATH in patients with diabetes hospitalized for Coronavirus disease(COVID-19).Ajusted model(Age + Sex).
* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 4 studies (Common effect model).
```{r analisis2a,include=TRUE}

meta2<-meta::metagen(TE=ROR_covid2$LOG_OR,
               seTE=ROR_covid2$SE_OR,
               studlab = ROR_covid2$COUNTRY2,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")

meta::forest(meta2,fontsize=8.2, boxsize=5, col.square="black", hetstat=TRUE,leftcols="studlab",rightcols=c("effect", "ci","w.fixed"),xlim=c(0.2, 5),
             squaresize=0.5,plotwidth=unit(9, "cm"),colgap=unit(3, "mm"))





```


## Meta_Analisi Associations of macrovascular complications -PVD- with UCI in patients with diabetes hospitalized for Coronavirus disease(COVID-19).Ajusted model(Age + Sex).
* In this  case, there is  not variability between the 3 studies, so we will accept the average effect of the 3 studies (Common effect model).
```{r analisis2b,include=TRUE}

meta2b<-meta::metagen(TE=ROR_covid2_uci$LOG_OR,
               seTE=ROR_covid2_uci$SE_OR,
               studlab = ROR_covid2_uci$COUNTRY2,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta2b,fontsize=8.2, boxsize=5, col.square="black", hetstat=TRUE,leftcols="studlab",rightcols=c("effect", "ci","w.fixed"),xlim=c(0.2, 5),
             squaresize=0.5,plotwidth=unit(9, "cm"),colgap=unit(3, "mm"))





```



## 3.3  	Meta-Analysis of Death/Uci/Imv ~ Macrovascular disease -PVD- + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease.

* UK.Model        Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes  + Microvascular disease..
* FRANCE.Model    Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes  + Microvascular disease..
* HM.Model        Death ~ Macrovascular disease + Age + Sex + Hypertension + "--------------"  + Microvascular disease.
* BCN.Model       Death ~ Macrovascular disease + Age + Sex + Hypertension + "--------------" + "---------------------"

* UK.Model        Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes  + Microvascular disease..
* FRANCE.Model    Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes  + Microvascular disease..
* HM.Model        Uci ~ Macrovascular disease + Age + Sex + Hypertension + "--------------"  + Microvascular disease.

* FRANCE.Model    imv ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes  + Microvascular disease..



## Meta_Analisi Associations of macrovascular complications-PVD- with DEATH in patients with diabetes hospitalized for Coronavirus disease(COVID-19).Ajusted model(Age + Sex + Hypertension + Type of Diabetes + Microvascular disease).
* In this  case, there is  not variability between the 4 studies, so we will accept the average effect of the 4 studies (Common effect model).

```{r analisis3a,include=TRUE}

meta3<-meta::metagen(TE=ROR_covid3$LOG_OR,
               seTE=ROR_covid3$SE_OR,
               studlab = ROR_covid3$COUNTRY2,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta3,fontsize=8.2, boxsize=5, col.square="black", hetstat=TRUE,leftcols="studlab",rightcols=c("effect", "ci","w.fixed"),xlim=c(0.2, 5),squaresize=0.5,plotwidth=unit(9, "cm"),colgap=unit(3, "mm"))



```

## Meta_Analisi Associations of macrovascular complications-PVD- with UCI in patients with diabetes hospitalized for Coronavirus disease(COVID-19).Ajusted model(Age + Sex + Hypertension + Type of Diabetes + Microvascular disease).
* In this  case, there is  not variability between the 3 studies, so we will accept the average effect of the 3 studies (Common effect model).

```{r analisis3b,include=TRUE}



meta3b<-meta::metagen(TE=ROR_covid3_uci$LOG_OR,
               seTE=ROR_covid3_uci$SE_OR,
               studlab = ROR_covid3_uci$COUNTRY2,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta3b,fontsize=8.2, boxsize=5, col.square="black", hetstat=TRUE,leftcols="studlab",rightcols=c("effect", "ci","w.fixed"),xlim=c(0.2, 5),squaresize=0.5,plotwidth=unit(9, "cm"),colgap=unit(3, "mm"))

```

## 3.4  	.

* UK.Model        Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* FRANCE.Model    Death ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.

* UK.Model        Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.
* FRANCE.Model    Uci ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.

* FRANCE.Model    Imv ~ Macrovascular disease + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia.


## Meta_Analisi Associations of macrovascular complications-PVD- with DEATH in patients with diabetes hospitalized for Coronavirus disease(COVID-19).Ajusted model(Meta-Analysis of Death ~ Macrovascular disease -PVD- + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia).
* In this  case, there is  not variability between the 2 studies, so we will accept the average effect of the 2 studies (Common effect model).

```{r analisis4a,include=TRUE}

meta4<-meta::metagen(TE=ROR_covid4$LOG_OR,
               seTE=ROR_covid4$SE_OR,
               studlab = ROR_covid4$COUNTRY2,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with death in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta4,fontsize=8.2, boxsize=5, col.square="black", hetstat=TRUE,leftcols="studlab",rightcols=c("effect", "ci","w.fixed"),xlim=c(0.2, 5),squaresize=0.5,plotwidth=unit(9, "cm"),colgap=unit(3, "mm"))



```

## Meta_Analisi Associations of macrovascular complications-PVD- with UCI in patients with diabetes hospitalized for Coronavirus disease(COVID-19).Ajusted model(Meta-Analysis of Uci ~ Macrovascular disease -PVD- + Age + Sex + Hypertension + Type of Diabetes + Microvascular disease + BMI + Etnia).
* In this  case, there is  not variability between the 2 studies, so we will accept the average effect of the 2 studies (Common effect model).

```{r analisis4b,include=TRUE}



meta4b<-meta::metagen(TE=ROR_covid4_uci$LOG_OR,
               seTE=ROR_covid4_uci$SE_OR,
               studlab = ROR_covid4_uci$COUNTRY2,
               sm = 'OR',
               title = "Meta_Analisi Associations of macrovascular complications with Uci in patients with diabetes hospitalized for Coronavirus disease(COVID-19)")


meta::forest(meta4b,fontsize=8.2, boxsize=5, col.square="black", hetstat=TRUE,leftcols="studlab",rightcols=c("effect", "ci","w.fixed"),xlim=c(0.2, 5),squaresize=0.5,plotwidth=unit(9, "cm"),colgap=unit(3, "mm"))

```


```



## 4. ANNEX: Macrovascular Complications Codes 


```{r codis_MACRO, include=T}




readxl::read_excel(conductor_codis2,col_types = "text")%>%dplyr::select(cod,Descripcio,agr,agr0,agr2)%>% filter(agr=="ARTER_PER")%>%dplyr::select(cod,agr)%>% knitr::kable(caption="ICD10 PERIPHERAL VASCULAR DISEASE Codes ")



```


# References


---
nocite: '@*'
...




&nbsp;
<hr />
<p style="text-align: center;">A work by $Jordi Real$ $Rai Puig$ </a></p>
<p style="text-align: center;">$Llepali System$ </a></p>
<p style="text-align: center;"><span style="color: #808080;"><em><https://github.com/USR-DAPCAT/></em></span></p>


